---
title: "Midterm Project Part Two"
author: "Madeline Greene"
output: html_document
---
<!-- Remember to set a custom THEME and HIGHLIGHTING in the YAML front matter above -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
### All libraries must be loaded in this chunk
### Any global options you'd like to set (a global ggplot theme for example) should go here
```



## Load Data

```{r}
## Read in and save your two tidy CSV files here for downstream use. 
## Show their output with head() for reproduciblity!
rawdata_path <- "/cloud/project/raw_data/exclusionExperimentData.xlsx" #defined the pathway to access the excel file sheet
read_excel(rawdata_path, "metaData") -> meta_data #renamed the datasheets so easier to access the data 
read_excel(rawdata_path, sheet = "algalDiversity") -> algal_diversity
read_excel(rawdata_path, sheet = "coralGrowth") -> coral_growth
read_excel(rawdata_path, sheet = "exclosureCover") -> exclosure_cover
read_excel(rawdata_path, sheet =  "plotBites") -> plot_bites
read_excel(rawdata_path, sheet = "recruitment") -> recruitment

#showing all outputs with head() as followed 
head(meta_data)
head(algal_diversity)
head(coral_growth)
head(exclosure_cover)
head(plot_bites)
head(recruitment)

```


## Figure W

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

## Figure X

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


## Figure Y

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**



## Figure Z

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


<!-- 
Remove the overall HTML comment if you want to do the bonus. 

## BONUS FIGURE

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

-->