---
title: "Midterm Project Part Two"
author: "Madeline Greene"
output: html_document
---
<!-- Remember to set a custom THEME and HIGHLIGHTING in the YAML front matter above -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

### All libraries must be loaded in this chunk
### Any global options you'd like to set (a global ggplot theme for example) should go here
```



## Load Data

```{r}
## Read in and save your two tidy CSV files here for downstream use. 
## Show their output with head() for reproduciblity!
read_csv("treatment_results.csv") -> treatment_results
head(treatment_results)
read_csv("plot_bites.csv") -> plot_bites
head(plot_bites)
```


## Figure 3B

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
plot_bites %>%
  filter(family == c("Acanthuridae", "Scaridae"), treatment == c("Full", "Partial", "Control")) %>% 
  #only need the two families according to previos graph and then filtered all treatment types
  select(treatment,family,timeCorrBites) -> new_bites_hour
  #out of all the columns, only needed treatment, family, and timeCorrBites

head(new_bites_hour)
#making sure it has all necessary components for graph
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
new_bites_hour %>%
  ggplot(aes(x = family, y= timeCorrBites)) +
  geom_jitter(aes(color=treatment), alpha=0.5)+ #used alpha so can guarentee seeing all of the points
  scale_color_brewer(palette= "Dark2") + #colorblind friendly palette
  labs(x = "Family", y = "Bites Per Minute", color = "Treatment") ->figure3b 
  #as per the metadata, it is by minute not hour

figure3b

```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

## Figure X

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


## Figure Y

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**



## Figure Z

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


<!-- 
Remove the overall HTML comment if you want to do the bonus. 

## BONUS FIGURE

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

-->