---
title: "Midterm Project Part Two"
author: "Madeline Greene"
output: html_document
---
<!-- Remember to set a custom THEME and HIGHLIGHTING in the YAML front matter above -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### All libraries must be loaded in this chunk
### Any global options you'd like to set (a global ggplot theme for example) should go here
```



## Load Data

```{r}
## Read in and save your two tidy CSV files here for downstream use. 
## Show their output with head() for reproduciblity!

```


## Figure W

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

## Figure X

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


## Figure Y

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**



## Figure Z

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**


<!-- 
Remove the overall HTML comment if you want to do the bonus. 

## BONUS FIGURE

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
```

```{r}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
```


Replace this text with a few sentences intepreting your figure, **according to the directions!**

-->