---
title: "Midterm Project Part Two"
author: "Madeline Greene"
output: 
  html_document:
    theme: united
    highlight: tango
    

---
<!-- Remember to set a custom THEME and HIGHLIGHTING in the YAML front matter above -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

### All libraries must be loaded in this chunk
### Any global options you'd like to set (a global ggplot theme for example) should go here
```



## Load Data

```{r}
## Read in and save your two tidy CSV files here for downstream use. 
## Show their output with head() for reproduciblity!
read_csv("treatment_results.csv") -> treatment_results
head(treatment_results)
read_csv("plot_bites.csv") -> plot_bites
head(plot_bites)
```


## Figure 3B

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.
plot_bites %>%
  filter(family == c("Acanthuridae", "Scaridae"), treatment == c("Full", "Partial", "Control")) %>% 
  #only need the two families according to previos graph and then filtered all treatment types
  mutate(bites_corr_hour = (timeCorrBites/60))%>%
  select(treatment,family, bites_corr_hour) -> new_bites_hour
  #out of all the columns, only needed treatment, family, and timeCorrBites

head(new_bites_hour)
#making sure it has all necessary components for graph
```

```{r, fig.width= 10, fig.height= 5 }
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk
new_bites_hour %>%
  ggplot(aes(x = family, y= bites_corr_hour)) +
  geom_jitter(aes(color=treatment), alpha=0.5)+ #used alpha so can guarantee seeing all of the points
  scale_color_brewer(palette= "Dark2") + #colorblind friendly palette
  labs(x = "Family", y = "Bites Per Hour", color = "Treatment") ->figure3b 


figure3b

```

The data here was very hard to interpret from the figure they provided us with. I believe that the metadata sheet and the figures did not correspond correctly with each other. When viewing the data, it appears that both families had a lot of the same results of 0 bites per minute. Because I am not knowledgeable about this specific data, I cannot tell if that is normal or an error of results. I changed it to per hour as the axis title which makes the data more understandable. I believe that a jitter plot was appropriate to display this data because it was able to show compare both families and provide exact points of the recorded data.  

## Figure 5B

```{r, fig.width= 4, fig.height=5}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.

treatment_results %>%
  filter(Species == "artCal") %>% 
  #only selecting articulated calcareous algae
  select(Species, treatment, Month, Year, Percent_cover) -> new_artcal_results
  #figure will need the species, month/year, percent cover

head(new_artcal_results)
#making sure it has all necessary components for figure
```

```{r, fig.width=10, fig.height=5}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk

new_artcal_results %>%
  ggplot(aes(x = Month, y = Percent_cover, fill= treatment)) +
  geom_boxplot(position = position_dodge2(width = 1)) +
  #would be able to show outliers in this form of graph as well as average
  facet_grid(~Year)+
  #wanted the years next to eachother to observe year difference
  scale_fill_brewer(palette= "Dark2") +
  #colorblind friendly palette 
  theme(strip.background = element_rect(fill = "honeydew3")) +
  #felt like switching up the header color
  labs(y = "Percent Cover (%)", fill = "Treatment") -> figure_5b

figure_5b
```


By viewing the boxplot that was just created, it shows that the full treatment has the highest values over the three types of treatments. This conclusion is the same as the original figure provided for this data. I believe that this form of visualization helps understand the data more than the original figure because it provides more information such as outliers and the mean. 


## Figure 6A

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.

treatment_results %>%
 mutate(Morph = case_when(morph == "mound.crust" ~ "Mounding & Encrusting Corals", morph == "branch" ~ "Branching Corals")) %>%
  drop_na(Morph) %>%
  #removed NAs
  select(- morph) %>%
  #removed column since created a new one with new names
  mutate(growth = growth * 100) %>%
  #after looking at data again and graph, realized that it was not in percent so needed to multiply by 100
  select(Morph, growth, treatment) -> new_morph
  #only shows what I will be graphing so it is cleaner to look like and when deciding how to wrangle data
  
new_morph
```

```{r, fig.width= 10, fig.height=5}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk

new_morph %>%
  ggplot(aes(x = Morph, y = growth, fill = treatment)) +
  geom_violin(alpha = 0.5) +
  #would show distribution of data/be able to properly see black line
  scale_fill_brewer(palette = "Dark2") +
  #colorblind friendly
  labs(y = "Change in Live Tissue Area (%)", fill = "Treatment") +
  geom_hline(yintercept = 0, col = "black")  -> figure_6a
  #had a black line go through the y intercept to show where there is 0 % change

figure_6a
```


This figure is significantly different from the figure provided in the paper. It provides more information than just the average with a standard deviation line. I used a violin plot to show the distribution of where there were changes in live tissue. I did in fact change my original wrangled data after initially plotting. When I first plotted, I noticed that the y values were -1 to 3. This would not make sense based on the data or representing a percent change. Therefore, I re-wrangled my data to make it a percent by multiplying by 100. The data looks different, probably because it is not an average and rather a distribution. In the original figure, it ranged from -100 to 100 but in this new figure, it ranges from -100 to 300. This is showing that it is true that their way of measuring means that is greater than 100% is possible due to multiple layers of covers.



## Figure 6B

```{r}
## Code to prepare data for plotting goes here. 
## It should save a dataset you can use to plot in the next chunk.

treatment_results %>%
  filter(Species == "totalAlgae") %>%
  #only plotting Algae totals
   mutate(Morph = case_when(morph == "mound.crust" ~ "Mounding & Encrusting Corals", morph == "branch" ~ "Branching Corals")) %>%
  drop_na(Morph) %>%
  #removed NAs
  select(- morph) %>%
  #removed column since created a new one with new names
  mutate(growth = growth * 100) %>%
  #made it a percent not decimal
  select(Morph, treatment, growth, Percent_cover) -> new_algal_cover
  #selected only columns that were needed 

new_algal_cover
```

```{r, fig.width= 10, fig.height=5}
## plot the data here.
## ensure an appropriate figure size and legible output by setting the fig.width and fig.height for this chunk

new_algal_cover %>%
  ggplot(aes(x = Percent_cover, y = growth, color = treatment)) +
  geom_point()+
  #scatterplot to show where data points are
  facet_grid(treatment~ Morph) +
  #wanted to separate morphs and treatments to better understand data
  scale_color_brewer(palette = "Dark2") +
  #colorblind friendly color
  labs(y = "Change in Live Tissue Area (%)", x = "Algal Cover (%)", color = "Treatment") +
  geom_smooth(method = "lm") -> figure_6b
  #made smooth trendlines

figure_6b
```


This figure is MUCH better for interpreting the data than the original one. This figure allows us to view the data by morph and treatment. By sectioning off each, it is easier to view and analyze. The control treatment had a low live tissue area change in relation to algal cover percent. There was one outlier at 300% change. The full treatment was the most spread out and had a large range of percent change and algal cover percentages. 
